Sailing the High Seas: A Christian Exploration of Piracy

### 2024-04-18 paper.tex
Finish some responses

\title{Sailing the High Seas:\\ A Christian Exploration of Piracy}
\author{Pedro J. Avalos Jim\'enez, Niklas Anderson}
\date{Wheaton College\\\today}

@@

\subsection{Background Information}

\blockcquote{barlow:wine}{%
  \textins{T}hat ideas should freely spread from one to another over the globe,
  for the moral and mutual instruction of man, and improvement of his
  condition, seems to have been peculiarly and benevolently designed by nature,
  when she made them, like fire, expansible over all space, without lessening
  their density at any point, and like the air in which we breathe, move, and
  have our physical being, incapable of confinement or exclusive appropriation.
  Inventions then cannot, in nature, be a subject of property.
  \emph{Thomas Jefferson}%
}

@@

\subsection{Thesis/Argument}

Piracy should not be hastily thrown aside.
Piracy is an excellent tool for disseminating information, services, content,
\&c. that may not have been available any other way.

@@

\subsubsection{Illegal content}
Piracy, as discussed above, provides a way to distribute illegal content. This
content is not always beneficial to society; research articles, art, movies, \&c.
are not the only sorts of content that a pirate may distribute. Piracy opens
the door for questionable and illegal content that may be harmful to society
or national security.

% TODO: Talk about ties to illegal organizations that are involved?

\subsubsection{Response}

@@

\subsubsection{Response}

@@

\subsection{Final Thoughts / Responses}

By far, one of the most common arguments raised against piracy, as highlighted previously,
is that piracy steals money from businesses because it demotivates people from paying for
their products and services. While this may be true in many cases, the reality is a little
more nuanced. Someone who chooses to pirate a product rather than purchase it may not have
bought the product in the first place if piracy was not an option. On top of that, if
someone really enjoys using the pirated version of a piece of software, they might choose
to pay for the legitimate version of it to support the developers and get new updates
faster. Even if the user refuses to pay for software, distributing the pirated version of
software helps popularize it. When something gets really popular, people want to try it
and that leads to more people who might decide to support the company who develops it by
purchasing the real version.

>>>>

\title{Sailing the High Seas: A Christian Exploration of Piracy}
\author{Pedro J. Avalos Jim\'enez, Niklas Anderson}
\date{Wheaton College\\\today}

@@

\subsection{Background Information}
\blockcquote{barlow:wine}{%
  \textins{T}hat ideas should freely spread from one to another over the globe,
  for the moral and mutual instruction of man, and improvement of his
  condition, seems to have been peculiarly and benevolently designed by nature,
  when she made them, like fire, expansible over all space, without lessening
  their density at any point, and like the air in which we breathe, move, and
  have our physical being, incapable of confinement or exclusive appropriation.
  Inventions then cannot, in nature, be a subject of property.
  \emph{Thomas Jefferson}%
}

@@

\subsection{Thesis/Argument}
Piracy should not be hastily thrown aside.
Piracy is an excellent tool for disseminating information, services, content,
\&c. that may not have been available any other way.

@@

\subsubsection{Illegal and Immoral Content}
Piracy, as discussed above, provides a way to distribute illegal content. This
content is not always beneficial to society; research articles, art, movies, \&c.
are not the only sorts of content that a pirate may distribute. Piracy opens
the door for questionable and illegal content that may be harmful to society
or national security. Since this paper aims to focus on a Christian exploration
of piracy, then this section will focus mostly on immoral content to build a
stronger argument against piracy that diversifies itself from an argument from
criminality (as was explored earlier in this paper).

There are few (if any) types of illegal content that rival that of child
pornography. It is a very sad reality, but this type of content is distributed
widely through the use of the Internet. Why and how this happens is perhaps out
of scope for this paper, but part of may be due to a sense of privacy and
anonymity that is fostered to an extreme in certain subcultures of the
Internet.~\cite[588]{prichard:subcultures} Research reveals that piracy and
piracy-adjacent tools provide the means to distribute this disgusting content
to unimaginable scales. Prichard et al explored this area of research, with
the following conclusions:
\blockcquote[593]{prichard:subcultures}{%
  Based on longitudinal data collected between August and November 2010, this
  study screened for the search terms that still appeared in the isoHunt Top
  300 list in November after being observed during August. In summary, the
  study found that 158/162 search terms related to infringing content, while
  3/162 search terms related to child pornography and 1/162 to bestiality%
}
The consistently widespread nature of this immoral and illegal content presents
a really compelling argument against piracy for Christians.

\subsubsection{Response}
As mentioned above, Christians should not quickly dismiss this argument against
piracy. The reality of the matter is that we are sinful creatures full of
evil thoughts (Matt. 15:9); we are in dire need of a savior to redeem us, not
by any good works because even our best works are like filthy rags (Isa. 64:6).
This argument is compelling because of its severity. A naive response would
argue that harmful content is distributed via the surface web and without
piracy anyways. The argument, however, holds in that piracy enables the
widespread nature of this content, so what is a proper response to this
argument? There may be ways to engage with piracy communities to self-regulate
or to build better communities, as is suggested by Prichard et
al.~\cite[595--596]{prichard:subcultures}

This may be an unsatisfactory and complex answer to a large and complex issue.
Piracy (namely in the form of torrenting) does, however, rely on peers to
seed the content, and if changes can be made in these subcultures of the
internet via evangelizing, perhaps there is hope for a better piracy community.

@@

\subsubsection{Response}
While this argument does hold in many cases, the economic reality is more
complex. The argument assumes that pirates would pay for the content if piracy
was not an option, but that assumption should be brought into question. As
argued earlier in this paper, piracy can be a means to control the market for
real change, and pirates maybe do not consider purchasing the content in the
first place.

On the other hand, it is not completely out of the question to imagine a
pirate coming back to some creator (whether that is an individual or a
business) to pay for the content when they are finally able to. As this paper
showed earlier, many pirates are those who do not have the means to pay for
some of the content that they pirate, but perhaps they would if/when they
could.

@@

\subsection{Final Thoughts / Responses}
By far, one of the most common arguments raised against piracy, as highlighted previously,
is that piracy steals money from businesses because it demotivates people from paying for
their products and services. While this may be true in many cases, the reality is a little
more nuanced. Someone who chooses to pirate a product rather than purchase it may not have
bought the product in the first place if piracy was not an option. On top of that, if
someone really enjoys using the pirated version of a piece of software, they might choose
to pay for the legitimate version of it to support the developers and get new updates
faster. Even if the user refuses to pay for software, distributing the pirated version of
software helps popularize it. When something gets really popular, people want to try it
and that leads to more people who might decide to support the company who develops it by
purchasing the real version.
